### 2021-05-14 MSE_paper.tex
First draft (s.t. examples)

Here $\bm{X}$ is the $n\times p$ model matrix, $\bm{Y}$ is the $n\times 1$ vector of responses; $\bm{\beta}$ is the $p\times 1$ vector of parameters corresponding to the model terms and $\bm{\varepsilon}$ are independent normally distributed random error terms with constant variance, i.e. $\bm{\varepsilon}\sim \mathcal{N}(\bm{0},\sigma^{2}\bm{I}_{n})$.

@@

\begin{equation}
\label{eq::back_trnt}
\bm{Y}=\bm{X_{t}\mu_{t}}+\bm{\varepsilon},
\end{equation}

@@

Some of the alternative approaches of combining several objectives would include generating the Pareto optimal set of designs -- the approach thoroughly described by \cite{Lu2011optimization}.  \cite{Stallings2015general}developed methodology for generalising eigenvalue-based criteria (e.g. $A$- and $E$-optimality) in a way that allows differing interest (expressed through the weights) among any set of estimable functions of the fitted model parameters. The introduced strategy reflects the aims of experimentation that are not traditionally accounted for but definitely are of interest. [Add 2 more references to compound optimality]

\section{Individual criteria construction}
\label{sec::criteria}
\input{compound_criterion}

\section{Restricted randomisation}
\label{sec::ms_experiments}
\input{ms_experiments}

@@

%% Criteria for blocked experiments as a special case of MS
\subsection{Criteria for blocked experiments}
\label{subsec::compound_blocked}
\input{compound_blocked}

>>>>

Here $\bm{X}$ is the $n\times p$ model matrix, $\bm{Y}$ is the $n\times 1$ vector of responses; $\bm{\beta}$ is the $p\times 1$ vector of parameters corresponding to the model terms and $\bm{\varepsilon}$ are independent normally distributed random error terms with constant variance: $\bm{\varepsilon}\sim \mathcal{N}(\bm{0},\sigma^{2}\bm{I}_{n})$.

@@

\begin{equation}
\label{eq::treatment_model}
\bm{Y}=\bm{X_{t}\mu_{t}}+\bm{\varepsilon},
\end{equation}

@@

Some of the alternative approaches of combining several objectives would include generating the Pareto optimal set of designs -- the approach thoroughly described by \cite{Lu2011optimization}.  \cite{Stallings2015general}developed methodology for generalising eigenvalue-based criteria (e.g. $A$- and $E$-optimality) in a way that allows differing interest (expressed through the weights) among any set of estimable functions of the fitted model parameters. The introduced strategy reflects the aims of experimentation that are not traditionally accounted for but definitely are of interest. [Add more references to compound optimality?]

\section{Individual criteria construction}
\label{sec::criteria}
\textit{	
	\begin{itemize}
		\item[-] Model misspecification setup. What objectives to be reflected in criteria: PE
		\item[-] Lack-of-fit criterion (and then the traditional LoF)
		\item[-] MSE criterion
		\item[-] Combining with DP/LP -- the general compound criterion
	\end{itemize}
}
\input{compound_criterion}

\section{Restricted randomisation}
\label{sec::restricted_randomisation}
\input{restricted_randomisation}

@@

%% Criteria for blocked experiments as a special case of MS

### 2021-05-14 compound_blocked.tex
First draft (s.t. examples)

Therefore, the submatrix of (\ref{eq::MSE_b}) corresponding to the primary terms is
\begin{align}
\label{eq::mesb_submatrix}
\mbox{MSE}(\bm{\hat{\tilde{\beta}}}_1|\bm{\tilde{\beta}})_{22}=&\sigma^2(\bm{X}'_{1}\bm{QX}_{1})^{-1}+(\bm{X}'_{1}\bm{QX}_{1})^{-1}\bm{X}'_{1}\bm{QX}_{2}\bm{\beta}_2\bm{\beta}'_2\bm{X}'_{2}\bm{QX}_{1}(\bm{X}'_{1}\bm{QX}_{1})^{-1}=\notag\\& \sigma^2\bm{\tilde{M}}^{-1}+\bm{\tilde{M}}^{-1}\bm{X}'_{1}\bm{QX}_{2}\bm{\beta}_2\bm{\beta}'_2\bm{X}'_{2}\bm{QX}_{1}\bm{\tilde{M}},^{-1}
\end{align}
where $\bm{\tilde{M}}=\bm{X}'_{1}\bm{QX}_{1}.$
\subsection{Determinant-based criterion}
As in the unblocked case (\ref{eq::MSE_det}), we construct the determinant-based criterion function to be minimised as the expectation of the logarithm of the determinant of the submatrix of the MSE matrix which was outlined above. First we see how its determinant looks:
\begin{align}
\label{eq::MSE_B_det}
\det[\mbox{MSE}(\bm{\hat{\tilde{\beta}}}_1|\bm{\tilde{\beta}})_{22}]=&\det[\sigma^2\bm{\tilde{M}}^{-1}+\bm{\tilde{M}}^{-1}\bm{X}'_{1}\bm{QX}_{2}\bm{\beta}_2\bm{\beta}'_2\bm{X}'_{2}\bm{QX}_{1}\bm{\tilde{M}}^{-1}]=\notag\\& \sigma^{2p}\det[\bm{\tilde{M}}^{-1}+\bm{\tilde{M}}^{-1}\bm{X}'_{1}\bm{QX}_{2}\bm{\tilde{\beta}}_2\bm{\tilde{\beta}}'_2\bm{X}'_{2}\bm{QX}_{1}\bm{\tilde{M}}^{-1}]=\notag\\& \sigma^{2p}\det[\bm{\tilde{M}}^{-1}](1+\bm{\tilde{\beta}}'_2\bm{X}'_{2}\bm{QX}'_{1}\bm{\tilde{M}}^{-1}\bm{X}'_{1}\bm{QX}_{2}\bm{\tilde{\beta}}_2).
\end{align}

>>>>

Therefore, the submatrix of (\ref{eq::MSE_b}) corresponding to the primary terms is
\begin{align}
\label{eq::mesb_submatrix}
\mbox{MSE}(\bm{\hat{\tilde{\beta}}}_1|\bm{\tilde{\beta}})_{22}=&\sigma^2(\bm{X}'_{1}\bm{QX}_{1})^{-1}+(\bm{X}'_{1}\bm{QX}_{1})^{-1}\bm{X}'_{1}\bm{QX}_{2}\bm{\beta}_2\bm{\beta}'_2\bm{X}'_{2}\bm{QX}_{1}(\bm{X}'_{1}\bm{QX}_{1})^{-1}=\notag\\& \sigma^2\bm{\tilde{M}}^{-1}+\bm{\tilde{M}}^{-1}\bm{X}'_{1}\bm{QX}_{2}\bm{\beta}_2\bm{\beta}'_2\bm{X}'_{2}\bm{QX}_{1}\bm{\tilde{M}},^{-1}
\end{align}
where $\bm{\tilde{M}}=\bm{X}'_{1}\bm{QX}_{1}.$

As in the unblocked case (\ref{eq::MSE_det}), we construct the determinant-based criterion function to be minimised as the expectation of the logarithm of the determinant of the submatrix of the MSE matrix which was outlined above. First we see how its determinant looks:
\begin{align}
\label{eq::MSE_B_det}
\det[\mbox{MSE}(\bm{\hat{\tilde{\beta}}}_1|\bm{\tilde{\beta}})_{22}]=&\det[\sigma^2\bm{\tilde{M}}^{-1}+\bm{\tilde{M}}^{-1}\bm{X}'_{1}\bm{QX}_{2}\bm{\beta}_2\bm{\beta}'_2\bm{X}'_{2}\bm{QX}_{1}\bm{\tilde{M}}^{-1}]=\notag\\& \sigma^{2p}\det[\bm{\tilde{M}}^{-1}+\bm{\tilde{M}}^{-1}\bm{X}'_{1}\bm{QX}_{2}\bm{\tilde{\beta}}_2\bm{\tilde{\beta}}'_2\bm{X}'_{2}\bm{QX}_{1}\bm{\tilde{M}}^{-1}]=\notag\\& \sigma^{2p}\det[\bm{\tilde{M}}^{-1}](1+\bm{\tilde{\beta}}'_2\bm{X}'_{2}\bm{QX}'_{1}\bm{\tilde{M}}^{-1}\bm{X}'_{1}\bm{QX}_{2}\bm{\tilde{\beta}}_2).
\end{align}
